Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-17 WSSSPE3/report/wg_main_user_community.tex
Section 5.10: No content change.
Section 5.10: itsy-bitsy mutations

Several books have been written about software communities:
\begin{itemize}
\item ``Art of Community'' by Jono Bacon~\cite{art-of-community}. We could consider distilling this for scientific software.
\item Iain Larmour, from EPSRC in the UK (EPSRC: https://www.epsrc.ac.uk/) (not sure who from mentioned UK Collaborative Computational Projects (CCP: http://ccp.ac.uk)
\end{itemize}

@@

Discussion revolved around a few questions: what is the benefit of having a ``community'' for software sustainability, what
practices and circumstances lead to having a community, how can funding help or hinder this process, and perhaps most
importantly how can best practices be described and distilled into a document that can help new projects.

@@

The most important next steps is a ``Best Practice'' document, which would describe what successful projects with engaged
communities look like, how to replicate this type of project, and look at end-of-life on a community project. Inputs to this
document would include a software community survey of high functioning communities such as R Open Science, Python SciPy,
OPeNDAP, and Unidata, with analysis of factors that feed into their success. Also references lik the ``Art of Community'' could
be adapted and summarized for the science software community.

Another next step would be increasing recognition of need for science software projects to focus on building and supporting
their user community. Good Software Engineering practices are not enough, and popular training like Software Carpentry does
not currently address this issue head on.

>>>>

Several books have been written about software communities: \choinote{only 1 book below}
\begin{itemize}

\item ``Art of Community'' by Jono Bacon~\cite{art-of-community}. We could
consider distilling this for scientific software.

\item Iain Larmour, from EPSRC in the UK (EPSRC: https://www.epsrc.ac.uk/) (not
sure who from mentioned UK Collaborative Computational Projects (CCP:
http://ccp.ac.uk) \choinote{Who is ``not sure who'' supposed to be?}

\end{itemize}

@@

Discussion revolved around a few questions: what is the benefit of having a
``community'' for software sustainability, what practices and circumstances lead
to having a community, how can funding help or hinder this process, and perhaps
most importantly, how can best practices be described and distilled into a
document that can help new projects.

@@

The most important next steps is a ``Best Practice'' document, which would
describe what successful projects with engaged communities look like, how to
replicate this type of project, and look at end-of-life on a community project.
Inputs to this document would include a software community survey of highly
functioning communities such as R Open Science, Python SciPy, OPeNDAP, and
Unidata, with analysis of factors that feed into their success. Also references
lik the ``Art of Community'' could be adapted and summarized for the science
software community.

Another next step would be increasing recognition of need for science software
projects to focus on building and supporting their user communities. Good software
engineering practices are not enough, and popular training like Software
Carpentry does not currently address this issue head on.
